Output Summary

### 2021-10-22 03-post-process/output-plots.Rmd
Update parameter summary boxplots in RMD

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_Pb[.]$", "Process SD")
```

@@

```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
my_boxplot("^sig_Lpi[.]$", "Process SD")
```

@@

```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot(sub_index("sig_Lphi_Pa_Mb[LH_type,pop]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
my_boxplot(sub_index("sig_Lphi_Pa_Mb[LH_type,pop]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
```

@@

```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("sig_Lphi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_nor, pop = "."), "Process SD", main = "NOR")
my_boxplot(sub_index("sig_Lphi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Process SD", main = "HOR")
```

@@

```{r lgr-to-ocean-bxp}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = c("NOR", "HOR"))
```

@@

```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("sig_Lpsi_O1_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR")
my_boxplot(sub_index("sig_Lpsi_O1_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR")
```

@@

```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("sig_Lpsi_O2_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR")
my_boxplot(sub_index("sig_Lpsi_O2_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR")
```

@@

```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among Population Correlation", ylim = c(-1,1), las = 2)
```

@@

```{r bon-to-lgr-bxp}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = c("NOR", "HOR"))
```

@@

```{r prespawn-surv-bxp}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
```

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "mvn-short"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_lPb[.]$", "Process SD")
my_boxplot("^rho_lPb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```

@@

```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
my_boxplot("^sig_Lpi[.]$", "Process SD")
my_boxplot("^rho_Lpi", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```

@@

```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
```

### Among-pop Correlation

```{r overwinter-survival-bxp3, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_fall), "Among-pop Correlation (Fall)", ticklabs = vcov_labels, las = 3)
my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_spring), "Among-pop Correlation (Spring)", ticklabs = vcov_labels, las = 3)
```

@@

```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_nor, pop = "."), "Process SD", main = "NOR")
my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_hor, pop = "."), "Process SD", main = "HOR")
```

### Among-pop Correlation

```{r trib-to-lgr-bxp3, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
```

@@

```{r lgr-to-ocean-bxp}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
```

@@

```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("sig_Lpsi_O1_Rb[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
my_boxplot(sub_index("sig_Lpsi_O1_Rb[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
```

### Among-pop Correlation

```{r age3-rho-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("rho_Lpsi_O1_Rb[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
my_boxplot(sub_index("rho_Lpsi_O1_Rb[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
```

@@

```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("sig_Lpsi_O2_Rb[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
my_boxplot(sub_index("sig_Lpsi_O2_Rb[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
```

### Among-pop Correlation

```{r age4-rho-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("rho_Lpsi_O2_Rb[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
my_boxplot(sub_index("rho_Lpsi_O2_Rb[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
```

@@

```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1), las = 2)
```

@@

```{r bon-to-lgr-bxp}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
```

@@

```{r prespawn-surv-bxp}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
my_boxplot("rho_Lphi_Sb_Sa", "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels)
```
